Synpotic Soil Characterization

### 2025-09-26 3-reports/manuscript_figures.Rmd
minor cleaning

## Make the base map
base_plot <- 
  ggplot() + 
  geom_sf(data = region) + 
  #   geom_sf_text(data = st_labels, aes(label = STUSPS))+
  geom_point(
    data = sites, aes(x, y),
    size = 2, color = "black")+
  # CB inset rectangle
  geom_rect(aes(xmin = -77.8, xmax = -74.5, ymin = 36.8, ymax = 40.5), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -74.5, xend = -70, y = 38, yend = 38), 
               color = "black", lwd = 0.75) + 
  # WLE inset rectangle
  geom_rect(aes(xmin = -84, xmax = -82, ymin = 41, ymax = 42), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -83, xend = -83, y = 42, yend = 44), 
               color = "black", lwd = 0.75) + 
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.0, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering)+
  xlim(-92, -67)+
  ylim(35, 49)+
#  scale_x_continuous(labels = NULL)+
#  scale_y_continuous(labels = NULL)+
  theme(legend.background = element_rect(fill = alpha("white", 0.0)), 
        legend.key = element_rect(fill = "transparent"), 
        legend.position = c(0.85, 0.1),
        axis.text = element_blank()) + 
  labs(x = "", y = "")+
  theme_void()+
  NULL

>>>>

## Make the base map
base_plot <- 
  ggplot() + 
  geom_sf(data = region) + 
  #   geom_sf_text(data = st_labels, aes(label = STUSPS))+
  geom_point(
    data = sites, aes(x, y),
    size = 2, color = "black")+
  # CB inset rectangle
  geom_rect(aes(xmin = -77.8, xmax = -74.5, ymin = 36.8, ymax = 40.5), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -74.5, xend = -70, y = 38, yend = 38), 
               color = "black", lwd = 0.75) + 
  # WLE inset rectangle
  geom_rect(aes(xmin = -84, xmax = -82, ymin = 41, ymax = 42), 
            fill = NA, color = "black", lwd = 0.75) +
  geom_segment(aes(x = -83, xend = -83, y = 42, yend = 44), 
               color = "black", lwd = 0.75) + 
  annotation_north_arrow(location = "tr", which_north = "true", 
                         pad_x = unit(0.0, "in"), pad_y = unit(0.2, "in"),
                         style = north_arrow_fancy_orienteering)+
  xlim(-92, -67)+
  ylim(35, 49)+
  theme(legend.background = element_rect(fill = alpha("white", 0.0)), 
        legend.key = element_rect(fill = "transparent"), 
        legend.position = c(0.85, 0.1),
        axis.text = element_blank()) + 
  labs(x = "", y = "")+
  theme_void()+
  NULL
